|

### 2023-01-11 paper.Rmd
Wed Jan 11 18:00:11 CET 2023: update-remote.sh

@@

![First Generation Median Training Error for variable number of hidden Neurons - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_neurons.png)

@@

![First Generation Median Training Error for variable number of hidden Layers - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_layers.png)

@@

# add new experiments for full runs here!
# ...
```

@@

``` {bash recreate_csv_file_benchmarkRWSymReg, include=FALSE}
/Users/rmn/miniconda3/envs/dataScience/bin/python /Users/rmn/github/master_thesis/data/summarize_finalFitness.py
```

```{r full_run_realWorldSymReg_performance, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
fig.pos="H"
knitr::kable(
  read.csv("/Users/rmn/github/master_thesis/data/summary_table_final_fit.csv", sep=","),
  caption="Performance - Real World Symbolic Regression Benchmark Problems"
)%>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")
```

<!-- Results for Energy Cooling Dataset  -->

```{bash compile_energyCooling_2hl_maxIndSize_fullRun_30gens, include=FALSE}
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/energyCooling_2hl_maxIndSize_fullRun_30gens/re_evaluate_energyCooling_2hl_maxIndSize_fullRun_30gens.sh
```

>>>>

```{bash executeFirstGenNBs, include=FALSE}
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/airfoil_firstGen/re_evaluate_airfoilFirstGen.sh
```

@@

![First Generation Median Training Error for variable number of hidden Neurons - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_neurons_6plots.png)

@@

![First Generation Median Training Error for variable number of hidden Layers - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_layers_6plot.png)

@@

# concrete
bash /Users/rmn/masterThesis/eda-gp-2020/experiments/concrete_2hl_maxIndSize_fullRun_30gens/re_evaluate_concrete_2hl_maxIndSize_fullRun_30gens.sh

# ...
```

@@

``` {bash recreate_csv_file_benchmarkRWSymReg, include=FALSE}
/Users/rmn/miniconda3/envs/dataScience/bin/python /Users/rmn/github/master_thesis/data/summarize_csv_files.py
```

```{r full_run_realWorldSymReg_fitness, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_final_fit_mean.csv",
  # "/Users/rmn/github/master_thesis/data/summary_table_final_fit_median.csv",  -> Use this path to summarize by median
  sep=",",
  colClasses = c("character", "numeric", "character", "numeric", "numeric", "character", "character")
)

# Create a new dataframe with the modified values of the two columns,
df_bold <- df

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "DAE.GP"],4)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df[i, "Pre.Trained_DAE.GP"],4))
    }
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "Pre.Trained_DAE.GP"],4)))
  df_bold[i, "DAE.GP"] <- as.character(round(df[i, "DAE.GP"],4))
  }
}
# shorten column names
col_names <- c("Problem", "Hidden-Layers", "Set", "DAE-GP", "Pre-Trained", "P-Value", "Cliffs-Delta")

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=TRUE ) %>% kableExtra::kable_styling(latex_options = "hold_position")

## Solution Size in Symbolic Regression

<!-- Overview Table  -->

```{r full_run_realWorldSymReg_best_solution_size, echo=FALSE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(knitr)
library(kableExtra)
library(dplyr)

# Create the data frame from csv
df <- read.csv(
  "/Users/rmn/github/master_thesis/data/summary_table_best_size_mean.csv",
  sep=",",
  colClasses = c("character", "numeric", "numeric", "numeric", "character", "character")
)

# Create a new dataframe with the modified values of the two columns,
df_bold <- df

for(i in 1:nrow(df)){
  if(df[i, "DAE.GP"] < df[i, "Pre.Trained_DAE.GP"]){
    df_bold[i, "DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "DAE.GP"],4)))
    df_bold[i, "Pre.Trained_DAE.GP"] <- as.character(round(df[i, "Pre.Trained_DAE.GP"],4))
    }
  else if (df[i, "DAE.GP"] > df[i, "Pre.Trained_DAE.GP"]) {
    df_bold[i, "Pre.Trained_DAE.GP"] <- sub("^(.*)$", "**\\1**", as.character(round(df[i, "Pre.Trained_DAE.GP"],4)))
  df_bold[i, "DAE.GP"] <- as.character(round(df[i, "DAE.GP"],4))
  }
}
# shorten column names
col_names <- c("Problem", "Hid.Layers", "DAE-GP", "Pre-Trained", "P-Value", "Cliffs-Delta")

knitr::kable(
 df_bold,
 format = "markdown",
 col.names = col_names,
 align = "c"
 #caption = "Symbolic Regression Overview - Mean final Fitness"
) %>% row_spec(0,bold=FALSE) %>% kableExtra::kable_styling(latex_options = "hold_position", font_size = 7)

<!-- Overview Plots  -->

\begin{tabular}{cc}
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/energyCooling_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/bostonHousing_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} \\
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/airfoil_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png} &
\includegraphics[width=0.45\textwidth]{~/masterThesis/master_thesis/img/concrete_2hl_maxIndSize_fullRun_30gens/mean_Size_byGens.png}
\end{tabular}
